HMM Model

### 2020-09-11 manuscript/competing_risks.Rmd
Additional models

theme_set(cowplot::theme_cowplot())
data <- read_data_for_analysis()
wide <- prepare_marker_data_wide(data)

@@

hypothesis_res_list[["competing_hcq_az_hospital"]] <-
  rbind(
  frequentist_hypothesis_res_from_coxph(hypotheses$hcq_reduces_death, fit_competing_hcq_az_hospital,
                                        coefficient_name = "took_hcqTRUE", transition = "1:3", adjusted = "age, sex, az"),
  frequentist_hypothesis_res_from_coxph(hypotheses$hcq_increases_discharged, fit_competing_hcq_az_hospital,
                                        coefficient_name = "took_hcqTRUE", transition = "1:2", adjusted = "age, sex, az")
  )
hypothesis_res_list[["competing_hcq_az_hospital"]]

@@

>>>>

theme_set(cowplot::theme_cowplot())
data <- read_data_for_analysis()
wide <- data$marker_data_wide

@@

hypothesis_res_list[["competing_hcq_az_hospital"]] <-
  rbind(
  frequentist_hypothesis_res_from_coxph(hypotheses$hcq_reduces_death, fit_competing_hcq_az_hospital,
                                        coefficient_name = "took_hcqTRUE", transition = "1:3", adjusted = "age, sex, az, hospital"),
  frequentist_hypothesis_res_from_coxph(hypotheses$hcq_increases_discharged, fit_competing_hcq_az_hospital,
                                        coefficient_name = "took_hcqTRUE", transition = "1:2", adjusted = "age, sex, az, hospital")
  )
hypothesis_res_list[["competing_hcq_az_hospital"]]

@@

```{r}
f_competing_hcq_az_comorbidities_sum <- update.formula(f_competing_hcq_az, . ~ . + comorbidities_sum)
fit_competing_hcq_az_comorbidities_sum <- coxph(f_competing_hcq_az_comorbidities_sum, data = data_surv, id = patient_id)
fit_competing_hcq_az_comorbidities_sum

hypothesis_res_list[["competing_hcq_az_comorbidities_sum"]] <-
  rbind(
  frequentist_hypothesis_res_from_coxph(hypotheses$hcq_reduces_death, fit_competing_hcq_az_comorbidities_sum,
                                        coefficient_name = "took_hcqTRUE", transition = "1:3", adjusted = "age, sex, az, comorbidities (sum)"),
  frequentist_hypothesis_res_from_coxph(hypotheses$hcq_increases_discharged, fit_competing_hcq_az_comorbidities_sum,
                                        coefficient_name = "took_hcqTRUE", transition = "1:2", adjusted = "age, sex, az, comorbidities (sum)")
  )
hypothesis_res_list[["competing_hcq_az_comorbidities_sum"]]
```

```{r}
hypothesis_res_all <- do.call(rbind, hypothesis_res_list)
write_csv(hypothesis_res_all, path = paste0(cache_dir, "/competing_risks_res.csv"))
```

### 2020-09-11 manuscript/hmm.Rmd
Additional models

```
```{r}
m2_formula <- ~ is_improve_one + is_death + mo(death_id) + (0 + is_worsen_one | worsen_one_id) + 
    (0 + is_improve_one | improve_one_id) + best_supportive_care * rate_group + took_hcq * rate_group + age_norm * rate_group + sex * rate_group
m2 <- brmshmmdata(m2_formula, series_data, 
                  m1_rate_data, m1_hidden_state_data, m1_initial_states, prior = m1_prior,
                  observed_state_data = m1_observed_state_data)

@@

@@

>>>>

```
```{r}
m1_epred_rect <- posterior_epred_rect(m1_fit)
m1_predicted_rect <- posterior_epred_to_predicted(m1_fit, m1_epred_rect)
m1_predicted <- posterior_rect_to_long(m1_fit, m1_predicted_rect)
```

```{r}
m1_predicted_df <- posterior_long_to_df(m1_fit$data, m1_predicted)

all_ids <- m1_fit$data$serie_data %>% select(hospital_id, .serie) %>% 
  distinct() %>% arrange(hospital_id) %>% pull(.serie)
step_size <- 6
for(step in 1:ceiling(length(all_ids) / step_size)) {
  series_id <- ((step - 1) * step_size + 1) : (step* step_size)

  posterior_state_plot(m1_predicted_df, all_ids[series_id], m1_fit$data) %>% print()

```{r}
pp_check_last_state(m1_fit, m1_predicted_rect) #TODO separately terminal and non-terminal states. Or "state at time t" - this should be coherent
pp_check_transitions_direction(m1_fit, m1_predicted_rect)
pp_check_transitions_direction(m1_fit, m1_predicted_rect, states_from = 2:6)
```

```{r}
m2_formula <- ~ is_improve_one + is_death + mo(death_id) + (0 + is_worsen_one | worsen_one_id) + 
    (0 + is_improve_one | improve_one_id) + best_supportive_care * rate_group + took_hcq * rate_group + age_norm * rate_group + sex * rate_group
m2 <- brmshmmdata(m2_formula, series_data, 
                  m1_rate_data, m1_hidden_state_data, m1_initial_states, prior = m1_prior,
                  observed_state_data = m1_observed_state_data)

@@

```{r}
m2_epred_rect <- posterior_epred_rect(m2_fit)
m2_predicted_rect <- posterior_epred_to_predicted(m2_fit, m2_epred_rect)
m2_predicted <- posterior_rect_to_long(m2_fit, m2_predicted_rect)
```

```{r}
m2_predicted_df <- posterior_long_to_df(m2_fit$data, m2_predicted)

all_ids <- m2_fit$data$serie_data %>% select(hospital_id, .serie) %>% 
  distinct() %>% arrange(hospital_id) %>% pull(.serie)
step_size <- 6
for(step in 1:ceiling(length(all_ids) / step_size)) {
  series_id <- ((step - 1) * step_size + 1) : (step* step_size)

  posterior_state_plot(m2_predicted_df, all_ids[series_id], m2_fit$data) %>% print()

```{r}
pp_check_last_state(m2_fit, m2_predicted_rect) #TODO separately terminal and non-terminal states. Or "state at time t" - this should be coherent
pp_check_transitions_direction(m2_fit, m2_predicted_rect)
pp_check_transitions_direction(m2_fit, m2_predicted_rect, states_from = 2:6)
```

@@

```{r}
m4_formula <- ~ is_improve_one + is_death + mo(death_id) + (0 + is_worsen_one | worsen_one_id) + 
    (0 + is_improve_one | improve_one_id) + best_supportive_care * rate_group + took_hcq * rate_group + took_az * rate_group + age_norm * rate_group + sex * rate_group + (rate_group | hospital_id)
m4 <- brmshmmdata(m4_formula, series_data, 
                  m1_rate_data, m1_hidden_state_data, m1_initial_states, prior = m1_prior,
                  observed_state_data = m1_observed_state_data)

m4_fit <- brmhmm(m4, cache_file = paste0(cache_dir,"/hcq_m4.rds"))

summary(m4_fit$brmsfit)
```

```{r}
m4_epred_rect <- posterior_epred_rect(m4_fit)
m4_predicted_rect <- posterior_epred_to_predicted(m4_fit, m4_epred_rect)
m4_predicted <- posterior_rect_to_long(m4_fit, m4_predicted_rect)
```

```{r}
m4_predicted_df <- posterior_long_to_df(m4_fit$data, m4_predicted)

all_ids <- m4_fit$data$serie_data %>% select(hospital_id, .serie) %>% 
  distinct() %>% arrange(hospital_id) %>% pull(.serie)
step_size <- 6
for(step in 1:ceiling(length(all_ids) / step_size)) {
  series_id <- ((step - 1) * step_size + 1) : (step* step_size)

  posterior_state_plot(m4_predicted_df, all_ids[series_id], m4_fit$data) %>% print()

```{r}
pp_check_last_state(m4_fit, m4_predicted_rect) #TODO separately terminal and non-terminal states. Or "state at time t" - this should be coherent
pp_check_transitions_direction(m4_fit, m4_predicted_rect)
pp_check_transitions_direction(m4_fit, m4_predicted_rect, states_from = 2:6)
```

## M5 -

```{r}
m5_formula <-  ~ is_improve_one + is_death + mo(death_id) + (0 + is_worsen_one | worsen_one_id) + 
    (0 + is_improve_one | improve_one_id) + best_supportive_care * rate_group + took_hcq * rate_group + age_norm * rate_group + sex * rate_group + (rate_group | hospital_id) + mo(comorbidities_sum) * rate_group
m5 <- brmshmmdata(m5_formula, series_data, 
                  m1_rate_data, m1_hidden_state_data, m1_initial_states, prior = m1_prior,
                  observed_state_data = m1_observed_state_data)

m5_fit <- brmhmm(m5, cache_file = paste0(cache_dir,"/hcq_m5.rds"))

summary(m5_fit$brmsfit)
```

```{r}
m5_epred_rect <- posterior_epred_rect(m5_fit)
m5_predicted_rect <- posterior_epred_to_predicted(m5_fit, m5_epred_rect)
m5_predicted <- posterior_rect_to_long(m5_fit, m5_predicted_rect)
```

```{r}
m5_predicted_df <- posterior_long_to_df(m5_fit$data, m5_predicted)

all_ids <- m5_fit$data$serie_data %>% select(hospital_id, .serie) %>% 
  distinct() %>% arrange(hospital_id) %>% pull(.serie)
step_size <- 6
for(step in 1:ceiling(length(all_ids) / step_size)) {
  series_id <- ((step - 1) * step_size + 1) : (step* step_size)

  posterior_state_plot(m5_predicted_df, all_ids[series_id], m5_fit$data) %>% print()

```{r}
pp_check_last_state(m5_fit, m5_predicted_rect) #TODO separately terminal and non-terminal states. Or "state at time t" - this should be coherent
pp_check_transitions_direction(m5_fit, m5_predicted_rect)
pp_check_transitions_direction(m5_fit, m5_predicted_rect, states_from = 2:6)
```
